%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage{hyperref}
% \hypersetup{
%   colorlinks = Black,
%   linkcolor=Blue,
%   citecolor=Blue,
%   urlcolor=Blue,
%   pagebackref=true,
%   implicit=false,
%   bookmarks=true,
%   bookmarksopen=true,
%   pdfdisplaydoctitle=true
% }
\usepackage{enumerate}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Ning Wang} % Your name
\address{Department of Computer Science, Rowan University}
%\address{} % Your address
\address{201 Mullica Hill Road, Glassboro, NJ 08028} % Your secondary addess (optional)
\address{(267)251--2698 \\ wangn@rowan.edu}

% Your phone number and email

\begin{document}
\begin{center}
\vspace{-5pt}
\url{http://users.rowan.edu/~wangn/}

%{http://users.rowan.edu/$\sim$wangn/}
\end{center}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
\item $\diamond$ {\bf Ph.D.}, Computer and Information Sciences  \hfill {\textit{09/2013 - 07/2018}} \\ 
\hspace{-20em} Temple University, Philadelphia, USA \hfill {\bf Advisor}: Jie Wu \\
{\bf Thesis}: Efficient  Routing and Offloading Schemes Design for Internet-of-Things Systems  \\
\vspace{-15pt}
\item $\diamond$ {\bf B.E.}, Electrical Engineering \hfill {\textit{09/2009 - 06/2013}} \\ 
University of Electronic Science and Technology of China (UESTC), Chengdu, China\\
%{\bf Project:} Studies on fast two-dimension terahertz raster scan imaging. %\hfill{M

\end{rSection}


\begin{rSection}{Employment}
\item $\diamond$ {\bf Assistant Professor}, Dept. of Computer Science  \hfill {\textit{09/2018 - now}} \\ 
\hspace{-20em} Rowan University, Glassboro, USA 
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Research}
\item $\diamond$ {\bf Research Interest}

My research interests belong to the broad category of Internet-of-Things systems with a focus on routing and performance optimization problems. Specific topics include: Opportunistic Mobile Networks, Mobile Edge Computing, Smart Cities, etc.

\item $\diamond$ {\bf Published Conference Papers}
\begin{enumerate}[{C}1.] \setlength{\itemsep}{-5pt}
\item S. Lu, J. Wu, Y. Duan, {\bf N. Wang}, and Z. Fang, ``Cost-Efficient Resource Provisioning in Delay-Sensitive Cooperative Fog Computing," \textit{Proc. of the 24th International Conference on Parallel and Distributed Systems (ICPADS 2018)}.
\item {\bf N. Wang} and J. Wu, ``{Optimal Cloud Instance Acquisition via IaaS Cloud Brokerage with Volume Discount}," \textit{Proc. of IEEE/ACM 26th International Symposium on Quality of Service ({\bf IWQoS'18})}.
\item {\bf N. Wang} and J. Wu, ``{Lag Minimization Through Optimal Player Matchmaking in Multi-Party Online Gaming}," \textit{Proc. of the 19th IEEE International Conference on a World of Wireless, Mobile and Multimedia Networks (WoWMoM'18)}.
\item {{\bf N. Wang} and J. Wu, ``{Optimal Data Partitioning and Forwarding in Opportunistic Mobile Networks},"} \textit{Proc. of the IEEE International Conference on International Conference on Communications (ICC'18)}.
\item {{\bf N. Wang} and J. Wu, ``{Optimal Cellular Traffic Offloading Through Opportunistic Mobile Networks by Data Partitioning},"} \textit{Proc. of the IEEE International Conference on Wireless Communications and Networking Conference (WCNC'18)}.
\item {{\bf N. Wang}, J. Wu, and P. Ostovari, ``{Coverage and Min-Max Workload Cost in Spatial Crowdsourcing},"} \textit{Proc. of the 14th IEEE International Conference on Ubiquitous Intelligence and Computing (UIC'17)}.
\item {{\bf N. Wang} and J. Wu, ``{Maximizing the User's Benefit in the Mobile Cloud Computing},"} \textit{Proc. of the MobiCom 8th ACM Wireless of the Students, by the Students, and for the Students Workshop (MobiCom S3'16)}.
\item {{\bf N. Wang} and J. Wu, ``{Mutually Exclusive Data Dissemination in the Mobile Publish/Subscribe System},"} \textit{Proc. of the 13th IEEE International Conference on Mobile Ad hoc and Sensor Systems (MASS'16)}.
\item {{\bf N. Wang} and J. Wu, ``{Minimizing the Subscription Aggregation Cost in the Content-based Pub/Sub System},"} \textit{Proc. of the 25th IEEE International Conference on Computer Communications and Networks (ICCCN'16)}.
\item {{\bf N. Wang} and J. Wu. ``{Opportunistic WiFi Offloading in a Vehicular Environment: Waiting or Downloading Now?},"} \textit{Proc. of the 35th IEEE International Conference on Computer Communications ({\bf INFOCOM'16}).} 
\item {{\bf N. Wang} and J. Wu. ``{Trajectory Scheduling for Timely Data Report in Underwater Wireless Sensor Networks},"} \textit{Proc. of the IEEE Global Communications Conference (GlOBECOM'15).} 
\item {{\bf N. Wang} and J. Wu. ``{A General Data and Acknowledgement Dissemination Scheme in Mobile Social Networks},"} \textit{Proc. of the 11th IEEE International Conference on Mobile Ad-hoc and Sensor Systems (MASS'14).} 
\item {{\bf N. Wang} and J. Wu. ``{InterestSpread: An Efficient Method for Content Transmission in Mobile Social Networks},"} \textit{Proc. of the 1st International Workshop on Mobile Sensing, Computing and Communication (MobiHoc MSCC'14).} 
\end{enumerate}

\item $\diamond$ {\bf Published Journal Papers}
\begin{enumerate}[{J}1.] \setlength{\itemsep}{-5pt}
%\setcounter{enumi}{12}
\item {{\bf N. Wang} and J. Wu, ``Cost-efficient Heterogeneous Coverage Requirement in Spatial Crowdsourcing,"} accepted to appear in \textit{{\bf IEEE Transactions on Big Data}}.
\item {{\bf N. Wang} and J. Wu, ``{Cost-Efficient Subscription Aggregation in the Content-Based Pub/Sub System},"} accepted to be appear in \textit{ Journal of Parallel and Distributed Computing}.
\item {{\bf N. Wang}, J. Wu and L. Sheng, ``{Rethink Data Forwarding in Mobile Social Networks using Movement History Information},"} accepted to appear in \textit{Ad Hoc \& Sensor Wireless Networks}.
\item H. Zheng, {{\bf N. Wang}, and J. Wu, ``{Minimizing Deep Sea Data Collection Delay with Autonomous Underwater Vehicles}," \textit{Journal of Parallel and Distributed Computing, Vol 104, 2017.}

\item {{\bf N. Wang} and J. Wu, ``{Data Dissemination in Mobile Social Networks with the Acknowledgment Feedback},"} \textit{Journal of Sensor and Actuator Networks}, Vol. 5, No. 2, 2016.}
\end{enumerate}


\item $\diamond$ {\bf Papers in Submission/Revision}
\begin{enumerate}[{N}1.] \setlength{\itemsep}{-5pt}
%\setcounter{enumi}{17}
\item  S. Lu, J. Wu, Y. Duan, {\bf N. Wang}, and Z. Fang,``Cost-Efficient Resource Provision for Multiple Mobile Users in Fog Computing", submitted to  \textit{the 16th IEEE  International Conference on Sensing, Communication and Networking (SECON'19)}.
\item H. Zheng,  {{\bf N. Wang}, and J. Wu,  ``Non-Submodularity and Approximability: Influence Maximization in Online Social Networks,"} submitted to \textit{the 20th IEEE International Conference on a World of Wireless, Mobile and Multimedia Networks (WoWMoM'19)}.
\item {{\bf N. Wang} and  J. Wu, ``Cost-Efficient Worker Trajectory Planning Optimization in Spatial Crowdsourcing Platform,"} submitted to \textit{the 20th International Symposium on Mobile Ad Hoc Networking and Computing (MobiHoc 2019)}.
\item {{\bf N. Wang} and J. Wu, ``Bundle Charging: Mobile Charging Trajectory Optimization."},  submitted to \textit{the 39th IEEE International Conference on Distributed Computing Systems (ICDCS'19)}. 
\item {\bf N. Wang} and J. Wu,  ``Latency Minimization Through Optimal Data Placement in Fog Computing", submitted to  Fog Computing: Theory and Practice, Wiley.
\end{enumerate}


\item $\diamond$ {\bf Invited Talks}
\begin{itemize}
    \item Efficient Routing and Offloading Design in Internet-of-Things Systems, Rowan University, Oct. 3rd, 2018
    \item Opportunistic Routing and Scheduling Design in Internet-of-Things Systems, University of Hartford, Feb. 4th, 2018.
\end{itemize}


\item $\diamond$ {\bf Students}
\begin{itemize}
    \item  Jeffrey Wang (undergraduate)
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%---------------------------------------------------------------------------------------

\begin{rSection}{Professional Activities}
$\diamond$  {\bf Program Committee Member}: 
\begin{itemize}
    \item 2019 International Conference of Distributed Computer Systems (ICDSCS'19)
\end{itemize}


$\diamond$ {\bf  Conference Reviewer}: 
\begin{itemize}
\item 2018 IEEE International Conference on Mobile Ad-hoc and Sensor Systems  (MASS'18)
\item 2018 International Conference on Big Data Computing and Communications (BIGCOM' 18)
\item 2018 IEEE Global Communications Conference  (GlOBECOM'18)
\item 2018 IEEE International Conference on Computer Communications and Networks (ICCCN'18)
\item  2016 IEEE International Conference on Distributed Computing Systems (ICDCS'16)
\item 2015 IEEE International Conference on Computer Communication (INFOCOM'15) \item 2015 IEEE International Conference on Sensing, Communication, and Conference (SECON'15)
\item 2015 IEEE International Conference on Mobile Ad-hoc and Sensor Systems (MASS'15) 
\item 2015 IEEE Global Communications Conference  (GlOBECOM'15) 
\item 2014 IEEE International Conference on Mobile Ad-hoc and Sensor Systems (MASS'14)
\end{itemize}

$\diamond$ {\bf Journal Reviewer}: 
\begin{itemize}
\item IEEE Network Magazine
\item IEEE Transactions on Mobile Computing
\item IEEE Transaction on Cloud Computing
\item IEEE Transactions on Intelligent Transportation Systems
\item IEEE Transactions on Wireless Communications
\item IEEE Transaction on Service Computing (TSC)
\item IEEE Access
\item Journal of Parallel and Distributed Computing (JPDC)
\item Journal of Computer Science and Technology (JCST)
\item International Journal of Ad Hoc and Ubiquitous Computing (IJAHUC)
\item Peer-to-Peer Networking and Applications
\item SCIENCE CHINA Information Sciences
\end{itemize}
\end{rSection}

\begin{rSection}{Teaching Experience}
$\diamond$ {\bf Instructor}: 
\begin{itemize}
	\item CS 06410: Data Communication/Networking (2019 spring, 1 section)
	\item CS 04225: Principles of Data Structures (2019 spring and 2018 fall, 2 sections)
	\item CS 06510: Computer Networks (2018 fall, 1 section)
\end{itemize}
$\diamond$ {\bf Teaching Assistant}: 

\begin{itemize}
	\item  CIS 2107: Computer Systems \& Low-Level Programming (2018 spring, 1 section)
	\item CIS 2168: Data Structures (2017 fall and 2017 spring, 3 sections)
	\item  CIS 3329: Network Architectures (2014 spring, 2014 fall, 2015 spring, and 2016 fall, 4 sections)
	\item  CIS 1068: Program Design and Abstraction (2015 fall, 3 sections)
	\item  CIS 3319: Wireless Networks and Security (2016 spring, 1 section)
\end{itemize}
\end{rSection}

\begin{rSection}{University and Department Services}
\begin{itemize}
	\item Computer Science Department Research Activity Committee Member \hfill \textit{2018 - now}
	\item Computer Science Department Industry Outreach Committee Member \hfill \textit{2018 - now}
%	\item CS 06510: Computer Networks (2018 fall, 1 section)
\end{itemize}
\end{rSection}



\begin{rSection}{AWARDS}
\begin{itemize}
	%{2nd prize in Feng Ru Imagine Cup} \hfill \textit{April 2011} \\
	\item {CIS Outstanding Graduate Teaching Assistant Award}  \hfill \textit{2018} \item  {Student travel grant award of the IEEE SmartWorld 2017}  \hfill \textit{2017} 
	\item {Student travel grant award of the IEEE MobiCom 2016}  \hfill \textit{2016} 
	\item {Student travel grant award of the IEEE INFOCOM 2016}  \hfill \textit{2016} 
    \item  {Student travel grant award of the IEEE MASS 2014}  \hfill \textit{2014} 
	\item {The excellent graduate of Sichuan Province, China}		\hfill \textit{2013} 
	%{The honor student of School of Physical Electronics} \hfill \textit{2013}\\
    \item {The Tang Lixin Scholarship, the most competitive scholarship in UESTC}						\hfill \textit{2012} 
\item  {The National Scholarship, China}							\hfill \textit{2011} 
	\item {The National Scholarship, China} 							\hfill \textit{2010}
	\end{itemize}
\end{rSection}

% \begin{rSection}{Technical Strengths}

% \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
% Computer Languages & Prolog, Haskell, AWK, Erlang, Scheme, ML \\
% Protocols \& APIs & XML, JSON, SOAP, REST \\
% Databases & MySQL, PostgreSQL, Microsoft SQL \\
% Tools & SVN, Vim, Emacs
% \end{tabular}

% \end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
